\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-29 paper/intro.tex
Refine footnote 1

Adopting the approach to third-party records search
taken by Bandits~\cite{sff-foci2014}\footnote{For the
purpose of anonymization, we present an anonymized version of this manuscript and
refer to the authors throughout as ``Bandits''.}, we
seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining} and show that both can 
be achieved in a privacy-preserving, accountable fashion.

>>>>

Adopting the approach to third-party records search
taken by Bandits~\cite{sff-foci2014}\footnote{Throughout this submission, we
cite an anonymized version of an existing paper on accountable surveillance
and use the pseudonym ``Bandits'' instead of the names of the authors.}, we
seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining} and show that both can 
be achieved in a privacy-preserving, accountable fashion.
